Modern type-safe embedding of attribute grammars

### 2018-12-10 doc/Paper.tex
Update PDF to a8bf478392329f3e8b9f53803fb39d81d3672f06

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Modern type-safe embedding of attribute grammars}
\subtitle{An exercise with functional zippers in Haskell}

@@

  % 1) Introduction. In one sentence, what’s the topic?
  % 2) State the problem you tackle
  % 3) Summarize (in one sentence) why nobody else has adequately answered the
  %    research question yet.
  % 4) Explain, in one sentence, how you tackled the research question.
  % 5) In one sentence, how did you go about doing the research that follows
  %    from your big idea.
  % 6) As a single sentence, what’s the key impact of your research?
\begin{abstract}
  Attribute grammars are a powerful, declarative formalism to implement and
  reason about programs which, by design, are conveniently modular. Although a
  full attribute grammar compiler can be tailored to specific needs, its
  implementation is highly non-trivial, and its long-term maintenance is a major
  endeavor. In fact, maintaining a traditional attribute grammar system is such
  a big effort that most systems that were proposed in the past are no longer
  active. Our approach to implementing attribute grammars is to write them as
  first-class citizens of a modern functional programming language. We improve a
  previous zipper-based attribute grammar embedding making it non-intrusive
  (i.e. no changes to the user-defined data types are required) and type-safe.
  On top of that, we achieve clearer syntax by using modern Haskell extensions.
  We believe that our embedding can be employed in practice to implement
  elegant, efficient, and modular solutions to real-life programming challenges.

\keywords{%
       Embedded Domain Specific Languages
  \and Zipper data structure
  \and Memoization
  \and Attribute Grammars
  \and Higher-Order Attribute Grammars
  \and Functional Programming%
}
\end{abstract}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Modern type-safe embedding of attribute grammars}
\subtitle{An exercise with functional zippers in Haskell\\--- Extended Abstract ---}

@@

  % 1) Introduction. In one sentence, what’s the topic?
  % 2) State the problem you tackle
  % 3) Summarize (in one sentence) why nobody else has adequately answered the
  %    research question yet.
  % 4) Explain, in one sentence, how you tackled the research question.
  % 5) In one sentence, how did you go about doing the research that follows
  %    from your big idea.
  % 6) As a single sentence, what’s the key impact of your research?
\section*{Abstract}
  Attribute grammars are a powerful, declarative formalism to implement and
  reason about programs which, by design, are conveniently modular. Although a
  full attribute grammar compiler can be tailored to specific needs, its
  implementation is highly non-trivial, and its long-term maintenance is a major
  endeavor. In fact, maintaining a traditional attribute grammar system is such
  a big effort that most systems that were proposed in the past are no longer
  active. Our approach to implementing attribute grammars is to write them as
  first-class citizens of a modern functional programming language. We improve a
  previous zipper-based attribute grammar embedding making it non-intrusive
  (i.e. no changes to the user-defined data types are required) and type-safe.
  On top of that, we achieve clearer syntax by using modern Haskell extensions.
  We believe that our embedding can be employed in practice to implement
  elegant, efficient, and modular solutions to real-life programming challenges.

\keywords{%
       Embedded Domain Specific Languages
  \and Zipper data structure
  \and Memoization
  \and Attribute Grammars
  \and Higher-Order Attribute Grammars
  \and Functional Programming%
}
%\end{abstract}
